====================================
## Introduction
The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. The following report describes how 
we built our model and how we used cross validation dataset. We will also use our prediction model to predict 20 different test cases at last.

## Data preparation
1.Load the datasets and libraries.
```{r warning=FALSE}
library(caret)
# Load datasets
trainRawData <- read.csv("pml-training.csv", header=TRUE, stringsAsFactors=FALSE)
testRawData <- read.csv("pml-testing.csv", header=TRUE, stringsAsFactors=FALSE)
```

2.Divide the data into two sets: training (70%) and cross validation (30%). The test set is given so there is no need to generate from the code.
```{r warning=FALSE}
set.seed(1234)
trainIndex <- createDataPartition(trainRawData$classe, p=0.7，list=FALSE)
# training dataset
training = trainRawData[trainIndex,]
# cross validation dataset
testing = trainRawData[-trainIndex,]
```

3.Filter the numeric variables and remove all the missing values in these variables
```{r warning=FALSE}
valid_idx = which(lapply(training,class) %in% "numeric")
validTrain<- preProcess(training[,valid_idx], method="knnImpute")
combTrain <- cbind(training$classe, predict(validTrain, training[,valid_idx]))
combTest <- cbind(testing$classe, predict(validTrain, testing[,valid_idx]))

# testing dataset
validSubmission <- predict(validTrain, testRawData[,valid_idx])
```

4.Rename first Label as classe
```{r warning=FALSE}
names(combTrain)[1] <- 'classe'
names(combTest)[1] <- 'classe'
```

## Prediction with Random Forest Model
Apply a random forest model to the numerical variables. 
```{r warning=FALSE}
library(randomForest)
modFit <- randomForest(classe ~ ., combTrain)
modFit
```

### In-sample accuracy
In-sample accuracy is 100%, which shows that the model does not suffer from bias. 
```{r warning=FALSE}
predictTrain <- predict(modFit, combTrain)
print(confusionMatrix(predictTrain, combTrain$classe))
```

### Out-of-sample accuracy
The out-of-sample accuracy is 98.6%, which is enough to predict the 20 test observations.
```{r warning=FALSE}
predictTest <- predict(modFit, combTest)
print(confusionMatrix(predictTest, combTest$classe))
```
 
## Test Set Prediction Results
Apply the model to the twenty test observations.
```{r warning=FALSE}
answers <- predict(modFit, validSubmission)
answers
```